Quantum Hoare Types

### 2019-09-12 paper/paper.tex
Use mathrm instead of textsf
Use mathpartir for multiple equations

%% Added by kartik
\usepackage[braket]{qcircuit}

@@

Recent work at Princeton as part of EPiQC\cite{DBLP:conf/oopsla/HuangM18,Huang:2019:SAV:3307650.3322213} has identified several classes of bugs in quantum programs and proposed approaches to tackle them. They proposed assertion checking using preconditions and post-conditions as one of the most effective techniques for most such classes of bugs.

@@

\abovedisplayskip=0pt
\belowdisplayskip=12pt

\[ \mathbf{H}(q_0) : \{ \mathrm{q\_state}(q_0) \in \{\ket{0}, \ket{1} \}\}\ r : \mathrm{unit}\ \{ \mathrm{q\_state}(q_0) \in \{\ket{+}, \ket{-}\} \} \]

\[ \mathbf{CNOT}(q_0, q_1) : \{ \mathrm{q\_state}(q_0) \in \{ \ket{+}, \ket{-} \} \wedge \mathrm{q\_state}(q_0) \in \{\ket{0}, \ket{1} \}\ r : \mathrm{unit}\ \{ \mathrm{entangled}(q_0, q_1) \}\]

@@

\begin{align*}
	b ::=&\ \textsf{true} \mid \textsf{false} \mid a1 = a2 \mid a1 \le a2\\
	\mid&\ \textsf{not}\ b \mid b1\ \textsf{and}\ b2
\end{align*}

@@

\begin{align*}
	c ::=&\ \textsf{SKIP} 														&\textsf{(do\ nothing)}\\
	\mid&\ x ::= a 															&\textsf{(assignment)}\\
	\mid&\ 1; ; c2 															&\textsf{(sequence)}\\
	\mid&\ \textsf{IFB}\ b\ \textsf{THEN}\ c1\ \textsf{ELSE}\ c2\ \textsf{FI} 	&\textsf{(conditional)}\\
	\mid&\ \textsf{WHILE}\ b\ \textsf{DO}\ c\ \textsf{END} 					&\textsf{(loop)}
\end{align*}

>>>>

%% Added by kartik
\usepackage[braket]{qcircuit}
\usepackage{mathpartir}

@@

Recent work at Princeton as part of EPiQC\footnote{EPiQC: Enabling Practical-Scale Quantum Computation:  \url{https://epiqc.cs.uchicago.edu}}\cite{DBLP:conf/oopsla/HuangM18,Huang:2019:SAV:3307650.3322213} has identified several classes of bugs in quantum programs and proposed approaches to tackle them. They proposed assertion checking using preconditions and post-conditions as one of the most effective techniques for most such classes of bugs.

@@

\begin{mathpar}
	\mathbf{H}(q_0) : \{ \mathrm{q\_state}(q_0) \in \{\ket{0}, \ket{1} \}\}\ r : \mathrm{unit}\ \{ \mathrm{q\_state}(q_0) \in \{\ket{+}, \ket{-}\} \}

	\\

	\mathbf{CNOT}(q_0, q_1) : \{ \mathrm{q\_state}(q_0) \in \{ \ket{+}, \ket{-} \} \wedge \mathrm{q\_state}(q_0) \in \{\ket{0}, \ket{1} \}\ r : \mathrm{unit}\ \{ \mathrm{entangled}(q_0, q_1) \}
\end{mathpar}

@@

\begin{align*}
	b ::=&\ \mathrm{true} \mid \mathrm{false} \mid a1 = a2 \mid a1 \le a2\\
	\mid&\ \mathrm{not}\ b \mid b1\ \mathrm{and}\ b2
\end{align*}

@@

\begin{align*}
	c ::=&\ \mathrm{SKIP}	&\mathrm{(do\ nothing)}\\
	\mid&\ x ::= a	&\mathrm{(assignment)}\\
	\mid&\ 1; ; c2	&\mathrm{(sequence)}\\
	\mid&\ \mathrm{IFB}\ b\ \mathrm{THEN}\ c1\ \mathrm{ELSE}\ c2\ \mathrm{FI}	&\mathrm{(conditional)}\\
	\mid&\ \mathrm{WHILE}\ b\ \mathrm{DO}\ c\ \mathrm{END}	&\mathrm{(loop)}
\end{align*}
